### 2020-12-03 analysis_and_paper/supplements.Rmd
Adds updated files following IPA at PS.

author: 
  - name          : Tobias Heycke
    affiliation   : 1, 2
    corresponding : yes    
    address       : "P.O. 122155, 68072 Mannheim, Germany"
    email         : "tobias.heycke@gesis.org"
  - name        : Frederik Aust
    affiliation : 1
  - name        : Mahzarin R. Banaji
    affiliation : 3
  - name        : John G. Conway
    affiliation : 4
  - name        : Pieter Van Dessel
    affiliation : 5
  - name        : Xiaoqing Hu
    affiliation : 6    
  - name        : Congjiao Jiang
    affiliation : 4    
  - name        : Benedek Kurdi
    affiliation : 3    
  - name        : Robert Rydell
    affiliation : 7
  - name        : Lisa Spitzer
    affiliation : 1
  - name        : Christoph Stahl
    affiliation : 1
  - name        : Christine A. Vitiello
    affiliation : 4
  - name        : Jan De Houwer
    affiliation : 5

affiliation:
  - id          : 1
    institution : University of Cologne
  - id          : 2
    institution : GESIS - Leibniz Institute for the Social Sciences
  - id          : 3
    institution : Harvard University 
  - id          : 4
    institution : University of Florida 
  - id          : 5
    institution : Ghent University 
  - id          : 6
    institution : The University of Hong Kong 
  - id          : 7
    institution : Indiana University

bibliography      : ["references.bib", "r-references.bib"]
#appendix          : "appendix.Rmd"

@@

@@

In the following we report additional analyses and provide details for the model specification used for the Bayesian model comparisons.
We report results from the linear mixed model analysis of the IAT response times, from prior sensitivity analyses for the Bayesian model comparisons, and from an exploratory analysis of the relationship between US recognition accuracy and associative learning.
Table\ \@ref(tab:otm1-participant-table) summarizes the participants' demographics separately for each location of data collection.

@@

The ANOVA of IAT scores reported in the main text ignores potential systematic trial-to-trial variability in IAT response latencies due to stimuli.
Any such systematic but unaccounted-for variance can inflate test statistics and yield underestimated $p$ values as well as underestimated confidence intervals.
We, therefore, also conducted a linear mixed model analysis of response times with crossed random effects for participants and items to ensure that our conclusion are not contingent on inadvertent stimulus effects [for details see @wolsiefer_modeling_2017].
For this analysis we excluded participants with error rates across all blocks larger than 50% or who responded faster than 300 ms on at least 10% of all trials.
We additionally discarded trials in which responses were faster than 400 ms or slower than 10 s.
These exclusion criteria are the same as those used by @wolsiefer_modeling_2017.

@@

We analyzed standardized response latencies, that is, the time that elapsed between stimulus presentation and *correct* response divided by the standard deviation of all response latencies in a given block, Figure\ \@ref(fig:otm1-iat-plot).
To assess the reversal of the response mapping effect, we contrasted the common response mapping of Bob and negative words with the common mapping of Bob and positive words.
Hence, larger values represent more favorable implicit evaluations.

@@

```{r otm1-iat-plot, fig.cap = "(ref:otm1-iat-plot)"}
otm1_results_legend <- guide_legend(
    # title = "Valence order\nDescriptions of Bob\n(Briefly presented primes)"
    title = expression(atop("Valence order", atop(scriptstyle("Learned behaviors"), scriptstyle("(Briefly presented USs)"))))
    , title.position = "top"
    , title.hjust = 0.5
    , reverse = TRUE
    , keyheight = 2
  )

@@

In line with the conventional ANOVA analysis, we found that response time differences suggested more favorable evaluations of Bob after the first than after the second block when the learned behaviors were first positive and later negative, `r otm1_iat_lmer_contrasts$full_result$Positive_negative`.
Vice versa, response time differences suggested more favorable evaluations after the second than after the first block when descriptions of Bob were first negative and later positive, `r otm1_iat_lmer_contrasts$full_result$Negative_positive`.
Again, these results indicate that the explicit evaluations and IAT scores were consistent.

@@

#### Explicit and implicit measures

@@

We, therefore, varied the scale for the Cauchy priors on the simple effects in the ranges of $`r min(replication_rscales$rating)` < r_\alpha < `r max(replication_rscales$rating)`$ and $`r min(replication_rscales$iat)` < r_\beta < `r max(replication_rscales$iat)`$ for rating and IAT scores, respectively.
Considering results previous studies, we limited our reanalysis to combinations where the prior scale was larger for rating than for IAT effects.
The results of the prior sensitvity analysis reassure us that our inference is robust to a wide range and combination of scales of the default Cauchy priors, see Table\ \@ref(tab:otm1-prior-sensitivity-replication-table).
The Bayes factors were not affected by the scale of the priors to any meaningful degree.
This is because our data are informative enough to overwhelm the priors and because these Bayes factors primarily depend on the shape and location of the posterior distribution, not the prior distributions [@klugkist_bayesian_2005].

@@

(ref:otm1-prior-sensitivity-replication-table-note) The Bayes factor (BF) in favor of $\mathcal{M}_\textrm{One mind}$ relative to $\mathcal{M}_\textrm{Any effect}$ is bounded within the range of $[0, 4]$ (see footnote 1 in the main article).
$r_\alpha$ and $r_\beta$ denote the scale for the Cauchy prior on the simple effects of learning block for rating scores ($\alpha$) and IAT scores ($\beta$), respectively (in units of standard deviations).

```{r otm1-prior-sensitivity-replication-table}
replication_rscales <- replication_rscales %>%
  printnum(format = c("f", "f", "e", "f")) %>%
  mutate(
    bf_one_mind_two_minds = papaja:::typeset_scientific(bf_one_mind_two_minds)
    , bf_one_mind_two_minds = paste0("$", bf_one_mind_two_minds, "$")
  ) %>%
  select(rating, everything())

@@

rec_bfs_res <- rec_bfs %>%
  printnum(digits = 2, format = "e") %>%
  papaja:::typeset_scientific()
```

@@

## Prime recogniton and implicit evaluations

@@

```{r otm1-rydell-recognition-plot, fig.cap = "(ref:otm1-rydell-recognition-plot)", fig.width = 3.5, fig.height = 2.5}
otm1_mem %>%
  ggplot(aes(x = Location, y = Accuracy, shape = Location, fill = Location)) +
  geom_hline(yintercept = 0.5, color = grey(0.5)) +
  geom_violin(alpha = 0.3) +
  # geom_point(position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.1)) +
  geom_sina(alpha = 0.5, size = 1) +
  # stat_summary(fun.y = mean, aes(group = Location, linetype = ValenceBlock), geom = "line", position = position_dodge(0.1), color = "black") +
  stat_summary(fun.data = mean_cl_boot, color = "black", fun.args = list(B = 10000)) +
  # scale_color_brewer(palette = "Set1", guide = otm1_results_legend) +
  # scale_fill_brewer(palette = "Set1", guide = otm1_results_legend) +
  scale_shape_manual(values = c(21, 23, 24)) +
  scale_color_manual(values = c(RColorBrewer::brewer.pal(3, "Set1"), "#000000")) +
  scale_fill_manual(values = c(RColorBrewer::brewer.pal(3, "Set1"), "#000000")) +
  labs(
    x = "Location"
    , y = "US recognition accuracy"
  ) +
  theme(legend.position = "none")
```

In contrast to the original results reported by @rydell_two_2006, US recognition accuracy in this study was above chance, Figure\ \@ref(fig:otm1-rydell-recognition-plot).
Memory for USs may, thus, have interfered with the associative learning process and prevented the predicted reversal of the IAT score differences.
We, therefore, performed an exploratory regression analysis of US recognition and the IAT score difference between blocks used in the Bayesian analysis above.
Positive values represent a more favorable evaluation after the block in which Bob was paired with positive learned behaviors and briefly presented negative USs.
Conversely, negative IAT score difference between blocks indicate that the IAT effects reflect the valence of the briefly presented USs.
If US recognition indeed obstructed the associative learning process, we would expect to observe a positive relationship between US recognition accuracy and IAT score differences between blocks:
When US recognition is high, IAT score differences should reflect the valence of the learned behaviors but not with the US valence.
We would expect to observe smaller and eventually negative IAT score differences as US recognition accuracy declines and associative learning takes over.

(ref:prime-recognition-iat-difference) Scatterplot of prime recognition accuracy and evaluative differences in IAT scores between blocks in which Bob was presented with positive descriptions and those in which he was paired with negative descriptions.

@@

otm1_iat_delta %>%
  ggplot(aes(x = Accuracy, y = delta)) +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_vline(xintercept = 0.5, linetype = "dotted") +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", color = "black") +
  labs(
    x = "US recognition accuracy"
    , y = expression("IAT score difference"~group("[", Delta~italic(z)~score, "]"))
  ) +
  theme_apa()
```

```{r prime-recognition-iat-difference-regression, results = "asis"}
otm1_recognition_iat_lm_bf <- otm1_iat_delta %>%
  filter(Measure == "IATscore") %>%
  mutate(Accuracy = Accuracy - 0.5) %>%
  as.data.frame %>%
  lmBF(delta ~ Accuracy, data = .) %>%
  apa_print

otm1_iat_delta_lm_res <- otm1_iat_delta %>%
  filter(Measure == "IATscore") %>%
  mutate(Accuracy = Accuracy - 0.5) %>%
  lm(delta ~ Accuracy, data = .) %>% 
  apa_print
```

However, we were unable to detect any relationship between US recognition accuracy and IAT score differences between blocks, `r otm1_iat_delta_lm_res$full_result$Accuracy`; the data even provide some evidence against such a relationship, `r otm1_recognition_iat_lm_bf$statistic`.
We centered US recognition at .5 and found that the intercept of the regression line was greater than zero, which indicates a positive IAT score difference despite at-chance US recognition accuracy, `r otm1_iat_delta_lm_res$full_result$Intercept`.
Hence, even for participants who exhibited no memory for briefly presented USs, IAT score differences reflected the valence of the learned behaviors, see Figure\ \@ref(fig:prime-recognition-iat-difference).
These results provide no indication that the deviation of our findings from those reported by @rydell_two_2006 are attributable to the above-chance US recognition accuracy in this study.

@@

>>>>

author: 
  - name          : Tobias Heycke
    affiliation   : "1,2"
    corresponding : yes    
    address       : "P.O. 122155, 68072 Mannheim, Germany"
    email         : "tobias.heycke@gesis.org"
    equal_contrib : yes
  - name          : Frederik Aust
    affiliation   : "1,9"
    equal_contrib : yes
  - name          : Mahzarin R. Banaji
    affiliation   : 3
  - name          : Jeremy Cone
    affiliation   : 8
  - name          : Pieter Van Dessel
    affiliation   : 5
  - name          : Melissa J. Ferguson
    affiliation   : 10
  - name          : Xiaoqing Hu
    affiliation   : 6    
  - name          : Congjiao Jiang
    affiliation   : 4    
  - name          : Benedek Kurdi
    affiliation   : "3,10"
  - name          : Robert Rydell
    affiliation   : 7
  - name          : Lisa Spitzer
    affiliation   : 1
  - name          : Christoph Stahl
    affiliation   : 1
  - name          : Christine Vitiello
    affiliation   : 4
  - name          : Jan De Houwer
    affiliation   : 5

affiliation:
  - id            : 1
    institution   : University of Cologne
  - id            : 2
    institution   : GESIS - Leibniz Institute for the Social Sciences
  - id            : 3
    institution   : Harvard University 
  - id            : 4
    institution   : University of Florida 
  - id            : 5
    institution   : Ghent University 
  - id            : 6
    institution   : The University of Hong Kong 
  - id            : 7
    institution   : Indiana University
  - id            : 8
    institution   : Williams College
  - id            : 9
    institution   : University of Amsterdam
  - id            : 10
    institution   : Yale University

bibliography      : ["references.bib", "r-references.bib"]

@@

In the following we report details on our power analyses, the model specifications used for the Bayesian model comparisons, and additional secondary analyses.

# Sensitivity of our design

```{r otm1-power-results}
som_cache <- "manuscript_cache/latex/"
rydell_pes <- knitr::load_cache(label = "rydell-effects", object = "rydell_pes", path = som_cache)
rydell_dz <- knitr::load_cache(label = "rydell-effects", object = "rydell_dz", path = som_cache)
otm1_n_power <- knitr::load_cache(label = "otm1-power", object = "otm1_n_power", path = som_cache) * 2
otm1_pes <- knitr::load_cache(label = "otm1-power", object = "otm1_pes", path = som_cache)
otm1_dz <- knitr::load_cache(label = "otm1-power", object = "otm1_dz", path = som_cache)

otm2_n_power <- knitr::load_cache(label = "otm2-omnibus-power", object = "otm2_n_power", path = som_cache) * 4
otm2_pes <- knitr::load_cache(label = "otm2-contrast-power", object = "otm2_pes", path = som_cache)
otm2_dz <- knitr::load_cache(label = "otm2-contrast-power", object = "otm2_dz", path = som_cache)
otm2_pes_between_collapsed <- knitr::load_cache(label = "otm2-contrast-power", object = "otm2_pes_between_collapsed", path = som_cache)
otm2_dz_between_collapsed <- knitr::load_cache(label = "otm2-contrast-power", object = "otm2_dz_between_collapsed", path = som_cache)
otm2_pes_collapsed <- knitr::load_cache(label = "otm2-contrast-power", object = "otm2_pes_collapsed", path = som_cache)
otm2_dz_collapsed <- knitr::load_cache(label = "otm2-contrast-power", object = "otm2_dz_collapsed", path = som_cache)
```

As noted in the main text, our assessment of the statistical senstivitiy of our design focused the tests of simple *learning block* effects, because they are of primary theoretical interest and less sensitive than the test of the interaction.
In Experiment 1, our planned contrasts had 95% power to detect learning block effects as small as $\delta_z = `r otm1_dz`$ ($\eta_p^2 = `r printp(otm1_pes)`$).
In Experiment 2, our planned contrasts had 95% power to detect learning block effects as small as $\delta_z = `r otm2_dz`$ ($\eta_p^2 = `r printp(otm2_pes)`$) or as small as $\delta_z = `r otm2_dz_between_collapsed`$ ($\eta_p^2 = `r printp(otm2_pes_between_collapsed)`$) and $\delta_z = `r otm2_dz_collapsed`$ ($\eta_p^2 = `r printp(otm2_pes_collapsed)`$) when pooling participants across one or both between-participant factors ($N = `r otm2_n_power * 4`$, $\alpha = .05$, two-sided tests).
Figure\ \@ref(fig:power-curve-plot) illustrates the implied sensitivity of our designs in units of Cohen's $\delta$ as a function of the assumed repeated-measures correlation $\rho$.
Note that these are conservative estimates as they do not take into account the additional 60 participants from our pilot study that we included in the analysis.

(ref:otm1-power-curve) Sensitivity curves for simple learning block effects in Experiment 1 (**A**) and Experiment 2 (**B**) as a function of the assumed repeated measures correlation.
Simple contrast are estimated within each *flashed word presentation duration*-*valence order* combination (not adjusted for multiple comparisons).
Collapsed contrasts pool participants across one or both  of the between subject factors (i.e., *flashed word presentation duration* and *valence order*).
$\delta_z$-values in the legend correspond to 95% and 80% power.
Note that these are conservative estimates as they do not take into account the additional 60 participants from our pilot study that we included in the analysis.
The grey dashed line at the top represents the smallest learning block difference reported by Rydell et al. [$d_z = `r rydell_dz`$; -@rydell_two_2006].

```{r power-curve-plot, fig.width = 7, fig.height = 8, fig.cap = "(ref:otm1-power-curve)"}
rydell_power_curve <- tibble(
  rho = seq(-1, 1, length.out = 100)
  , delta = c(
    dz_to_f(rydell_dz, unique(rho)) * 2
    # dz_to_f(mean(heycke_dz), unique(rho)) * 2
  )
  , power = NA
)

otm1_power_curve <- tibble(
  rho = rep(seq(-1, 1, length.out = 100), 2)
  , delta = c(
    dz_to_f(otm1_dz, unique(rho)) * 2
    , dz_to_f(otm1_dz2, unique(rho)) * 2
  )
  , power = rep(c("0.95", "0.80"), each = length(rho)/2)
)

otm1_power_curve_plot <- otm1_power_curve %>% 
  mutate(
    power = relevel(factor(power), "0.95")
  ) %>% 
  ggplot(aes(x = rho, y = delta, group = power, linetype = power)) +
  # ggplot(aes(x = rho, y = delta, color = power, group = power)) +
  geom_line(data = rydell_power_curve, aes(group = power), color = grey(0.8), linetype = "dashed") +
  geom_line() +
  # annotate("text", x = 1, y = 0.9, label = paste0("list(alpha ==~\".05\", italic(N) ==", otm1_n, ", epsilon == 1)"), parse = TRUE, hjust = 1, vjust = 0.5) +
  ylim(c(0, 1)) +
  scale_linetype_discrete(
    labels = c(
      bquote(.(unique(otm1_power_curve$power)[1])~~(delta[z] == .(printnum(otm1_dz))))
      , bquote(.(unique(otm1_power_curve$power)[2])~~(delta[z] == .(printnum(otm1_dz2))))
    )
  ) +
  labs(
    x = bquote("Correlation between learning blocks ["*rho*"]")
    , y = bquote("Learning block difference [Cohen's"~delta*"]")
    , color = "Contrast"
    , linetype = bquote("Power"~"["*1 - beta*"]")
  ) +
  ggtitle("", subtitle = bquote(list(italic(N) == .(otm1_n_power*2), alpha ==~".05", "two-sided"))) +
  theme_apa(box = TRUE) + 
  theme(
    panel.grid.major.x = element_line()
    , panel.grid.major.y = element_line()
    , panel.grid.minor.x = element_line()
    , panel.grid.minor.y = element_line()
    # , legend.position = c(0.99, 0.99)
    , legend.justification = "top"
    # , legend.background = element_rect(fill = scales::alpha("white", 0.5))
  )

rydell_power_curve <- tibble(
  rho = seq(-1, 1, length.out = 100)
  , delta = c(
    dz_to_f(rydell_dz, unique(rho)) * 2
    # dz_to_f(mean(heycke_dz), unique(rho)) * 2
  )
  , power = NA
)

otm1_power_curve <- tibble(
  rho = rep(seq(-1, 1, length.out = 100), 2)
  , delta = c(
    dz_to_f(otm1_dz, unique(rho)) * 2
    , dz_to_f(otm1_dz2, unique(rho)) * 2
  )
  , power = rep(c("0.95", "0.80"), each = length(rho)/2)
)

otm2_power_curve_plot <- tibble(
  rho = rep(seq(-1, 1, length.out = 100), 2)
  , otm2_delta_simple = c(
    dz_to_f(otm2_dz, unique(rho)) * 2
    , dz_to_f(otm2_dz2, unique(rho)) * 2
  )
  , otm2_delta_between_collapsed = c(
    dz_to_f(otm2_dz_between_collapsed, unique(rho)) * 2
    , dz_to_f(otm2_dz2_between_collapsed, unique(rho)) * 2
  )
  , otm2_delta_collapsed = c(
    dz_to_f(otm2_dz_collapsed, unique(rho)) * 2
    , dz_to_f(otm2_dz2_collapsed, unique(rho)) * 2
  )
  , power = rep(c("0.95", "0.80"), each = length(rho)/2)
) %>% 
  pivot_longer(cols = matches("otm"), names_to = "contrast", values_to = "delta") %>%
  mutate(
    power = relevel(factor(power), "0.95")
    , contrast = gsub("otm2_delta_", "", contrast)
    , contrast = gsub("_", " ", contrast)
    , contrast = factor(contrast, levels = c("simple", "between collapsed", "collapsed"))
  ) %>% 
  ggplot(aes(x = rho, y = delta, color = contrast, group = interaction(power, contrast), linetype = power)) +
  # ggplot(aes(x = rho, y = delta, color = power, group = power)) +
  # geom_line(data = otm1_power_curve, aes(group = power, linetype = power, color = "simple"), alpha = 0.3) +
  geom_line(data = rydell_power_curve, aes(group = power), color = grey(0.8), linetype = "dashed") +
  geom_line() +
  scale_color_viridis_d(
    end = 0.8
    , labels = c(
      bquote("Simple               "~delta[z] %in% "{"*.(printnum(otm2_dz))*", "*.(printnum(otm2_dz2))*"}")
      , bquote("Collapsed once   "~delta[z] %in% "{"*.(printnum(otm2_dz_between_collapsed))*", "*.(printnum(otm2_dz2_between_collapsed))*"}")
      , bquote("Collapsed twice   "~delta[z] %in% "{"*.(printnum(otm2_dz_collapsed))*", "*.(printnum(otm2_dz2_collapsed))*"}")
    )
  ) +
  ylim(c(0, 1)) +
  labs(
    x = bquote("Correlation between learning blocks ["*rho*"]")
    , y = bquote("Learning block difference [Cohen's"~delta*"]")
    , color = "Contrast"
    , linetype = bquote("Power"~"["*1 - beta*"]")
  ) +
  ggtitle("", subtitle = bquote(list(italic(N) == .(otm2_n_power*4), alpha ==~".05", "two-sided"))) +
  theme_apa(box = TRUE) + 
  theme(
    panel.grid.major.x = element_line()
    , panel.grid.major.y = element_line()
    , panel.grid.minor.x = element_line()
    , panel.grid.minor.y = element_line()
    # , legend.position = c(0.99, 0.99)
    , legend.justification = "top"
    # , legend.background = element_rect(fill = scales::alpha("white", 0.5))
  )

plot_grid(
  plot_grid(otm1_power_curve_plot, NULL, rel_widths = c(1, 1 - 5.65/7))
  , otm2_power_curve_plot
  , nrow = 2
  , ncol = 1
  , labels = "AUTO"
)
```

@@

In the following we report details on our power analysis, the model specification used for the Bayesian model comparisons, and additional secondary analyses.
We report results from the linear mixed model analysis of the IAT response times, from prior sensitivity analyses for the Bayesian model comparisons, and from an exploratory analysis of the relationship between the recognition accuracy of briefly flashed words and indirectyl measured evaluations.
Table\ \@ref(tab:otm1-participant-table) summarizes the participants' demographics separately for each location of data collection.

@@

The ANOVA of IAT scores reported in the main text ignores potential systematic trial-to-trial variability in IAT response latencies due to stimuli.
Any such systematic but unaccounted-for variance can inflate test statistics and yield anticonservative $p$ values as well as underestimated confidence intervals.
We, therefore, also conducted a linear mixed model analysis of response times with crossed random effects for participants and items to ensure that our conclusion are not contingent on inadvertent stimulus effects [for details see @wolsiefer_modeling_2017].
For this analysis we excluded participants with error rates across all blocks larger than 50% or who responded faster than 300 ms on at least 10% of all trials.
We additionally discarded trials in which responses were faster than 400 ms or slower than 10 s.
These exclusion criteria are the same as those used by @wolsiefer_modeling_2017.

@@

We analyzed standardized response latencies, that is, the time that elapsed between stimulus presentation and *correct* response divided by the standard deviation of all response latencies in a given block, Figure\ \@ref(fig:otm1-iat-plot).
To assess the reversal of the response mapping effect, we contrasted the common response mapping of Bob and negative words with the common mapping of Bob and positive words.
Hence, larger values indicate more favorable evaluations.

@@

```{r otm1-iat-plot, fig.cap = "(ref:otm1-iat-plot)"}
otm1_results_legend <- guide_legend(
    # title = "Valence order\nDescriptions of Bob\n(Briefly presented primes)"
    title = expression(atop("Valence order", atop(scriptstyle("Behavioral information"), scriptstyle("(Briefly flashed words)"))))
    , title.position = "top"
    , title.hjust = 0.5
    , reverse = TRUE
    , keyheight = 2
  )

@@

Also in line with the ANOVA analysis, we found that response time differences indicated *more* favorable evaluations after the first than after the second block when the behavioral information was first positive and later negative, `r otm1_iat_lmer_contrasts$full_result$Positive_negative`.
Vice versa, response time differences indicated *less* favorable evaluations after the first than after the second block when descriptions of Bob were first negative and later positive, `r otm1_iat_lmer_contrasts$full_result$Negative_positive`.
Again, these results indicate that the rating and IAT scores did not dissociate.

@@

#### Directly and indirectly measured evaluations

@@

We, therefore, varied the scale for the Cauchy priors on the simple effects in the ranges of $`r min(replication_rscales$rating)` < r_\alpha < `r max(replication_rscales$rating)`$ and $`r min(replication_rscales$iat)` < r_\beta < `r max(replication_rscales$iat)`$ for rating and IAT scores, respectively.
In light of the results from previous studies, we limited our analysis to combinations where the prior scale was larger for rating than for IAT effects.
The results of the prior sensitvity analysis reassure us that our inference is robust to a wide range and combination of scales of the default Cauchy priors, see Table\ \@ref(tab:otm1-prior-sensitivity-replication-table).
The Bayes factors were not affected by the scale of the priors to any meaningful degree.
This is because our data are informative enough to overwhelm the priors and because these Bayes factors primarily depend on the shape and location of the joint posterior distribution [@klugkist_bayesian_2005].

@@

(ref:otm1-prior-sensitivity-replication-table-note) The Bayes factor (BF) in favor of $\mathcal{M}_\textrm{One mind}$ relative to $\mathcal{M}_\textrm{Any effect}$ is bounded within the range of $[0, 4]$.
$r_\alpha$ and $r_\beta$ denote the scale for the Cauchy prior on the simple effects of learning block for rating scores ($\alpha$) and IAT scores ($\beta$), respectively (in units of standard deviations).

```{r otm1-prior-sensitivity-replication-table}
replication_rscales <- replication_rscales %>%
  printnum(format = c("f", "f", "e", "f")) %>%
  mutate(
    bf_one_mind_two_minds = papaja:::typeset_scientific(bf_one_mind_two_minds)
    # , bf_one_mind_two_minds = paste0("$", bf_one_mind_two_minds, "$")
  ) %>%
  select(rating, everything())

@@

rec_bfs_res <- rec_bfs %>%
  printnum(digits = 2, format = "e") %>%
  papaja:::typeset_scientific() %>%
  papaja:::strip_math_tags()
```

@@

## Word recogniton and IAT score differences

@@

```{r otm1-rydell-recognition-plot, fig.cap = "(ref:otm1-rydell-recognition-plot)", fig.width = 3.5, fig.height = 2.5}
otm1_mem %>%
  ggplot(aes(x = Location, y = Accuracy, shape = Location, fill = Location)) +
  geom_hline(yintercept = 0.5, color = grey(0.5)) +
  geom_violin(alpha = 0.3) +
  # geom_point(position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.1)) +
  geom_sina(alpha = 0.5, size = 1) +
  # stat_summary(fun.y = mean, aes(group = Location, linetype = ValenceBlock), geom = "line", position = position_dodge(0.1), color = "black") +
  stat_summary(fun.data = mean_cl_boot, color = "black", fun.args = list(B = 10000)) +
  # scale_color_brewer(palette = "Set1", guide = otm1_results_legend) +
  # scale_fill_brewer(palette = "Set1", guide = otm1_results_legend) +
  scale_shape_manual(values = c(21, 23, 24)) +
  scale_color_manual(values = c(RColorBrewer::brewer.pal(3, "Set1"), "#000000")) +
  scale_fill_manual(values = c(RColorBrewer::brewer.pal(3, "Set1"), "#000000")) +
  labs(
    x = "Location"
    , y = "Recognition accuracy"
  ) +
  theme(legend.position = "none")
```

In contrast to the original results reported by @rydell_two_2006, the recognition accuracy of briefly flashed words was above chance in this study, Figure\ \@ref(fig:otm1-rydell-recognition-plot).
Memory for these words may, thus, have interfered with the associative learning process and prevented the predicted reversal of IAT score differences between learning blocks.
We, therefore, performed an exploratory regression analysis of IAT score difference and recognition accuracy of briefly flashed words.
Positive IAT score differences indicate a more favorable evaluation after the block in which we presented positive behavioral information and briefly flashed negative words.
If word recognition indeed obstructed the associative learning process, we would expect to observe a positive relationship between the recognition accuracy and IAT score differences between blocks:
When the recognition for briefly flashed words is high, IAT score differences should be positive, that is reflect the valence of the behavioral information.
We would expect to observe smaller and eventually negative IAT score differences as the recognition accuracy declines and associative learning takes over.
To account for measurement error in the recognition accuracy of briefy flashed words we fit an errors-in-variable regression model [@Klauer_Draine_Greenwald_1998].
Because the model assumes that predictor values are sampled from a Gaussian distribution truncated at 0, we probit-transformed the recognition accuracy.^[A standard linear regression analysis yielded the same results.]

(ref:prime-recognition-iat-difference) Scatterplot of the recognition accuracy of briefly flashed words (on probit scale) and evaluative differences in IAT scores between learning blocks in which Bob was presented with positive descriptions and those in which he was paired with negative descriptions.
The regression line and confidence band represents predictions of the errors-in-variables model [@Klauer_Draine_Greenwald_1998].

@@

otm1_iat_delta %>%
  ggplot(aes(x = Accuracy, y = delta)) +
  geom_hline(yintercept = 0, linetype = "22") +
  geom_vline(xintercept = 0.5, linetype = "22") +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "eiv_lm", color = "black") +
  # geom_smooth(method = "lm", color = "black") +
  labs(
    x = bquote("Recognition accuracy ["~Phi^-1*(italic(p))~"]")
    , y = expression("IAT score difference"~group("[", Delta~italic(z)~score, "]"))
  ) +
  scale_x_continuous(trans = "probit") +
  theme_apa()
```

```{r prime-recognition-iat-difference-regression, results = "asis"}
# otm1_recognition_iat_lm_bf <- otm1_iat_delta %>%
#   filter(Measure == "IATscore") %>%
#   mutate(Accuracy = Accuracy - 0.5) %>%
#   as.data.frame %>%
#   lmBF(delta ~ Accuracy, data = .) %>%
#   apa_print
# 
# otm1_iat_delta_lm_res <- otm1_iat_delta %>%
#   filter(Measure == "IATscore") %>%
#   mutate(Accuracy = Accuracy - 0.5) %>%
#   lm(delta ~ Accuracy, data = .) %>% 
#   apa_print

otm1_iat_delta_eiv_lm_res <- otm1_iat_delta %>%
  filter(Measure == "IATscore") %>%
  mutate(Accuracy = qnorm(Accuracy)) %>%
  eiv_lm(delta ~ Accuracy, data = ., n.optim = 10) %>% 
  apa_print
```

We did not detect a relationship between the recognition accuracy of briefly preseted words and IAT score differences between learning blocks, `r otm1_iat_delta_eiv_lm_res$full_result$Accuracy`.
Moreover, the positive intercept of the regression line indicates a positive IAT score difference despite at-chance word recognition accuracy, `r otm1_iat_delta_eiv_lm_res$full_result$Intercept`.
Hence, even for participants who did not recognize the briefly flashed words, IAT score differences reflected the valence of the behavioral information, see Figure\ \@ref(fig:prime-recognition-iat-difference).
These results provide no indication that the deviation of our findings from those reported by @rydell_two_2006 are attributable to the above-chance recognition of briefly flashed words in this study.

@@

```{r create_r-references}
r_refs(file = "r-references.bib")
```
